Draft

### 2022-06-17 ms.tex
Sec.2 revised, ref to be added

\vspace{2mm}
\subsection{Seeds}\label{sec:seed}
The QLFs at high redshifts are determined by the original BH seeding and subsequent growth. 
Firstly we describe our model regarding the formation of BH seeds in progenitor DM halos 
that end up in high-$z$ quasar host galaxies with halo masses of $\Mh>10^{11}~\Msun$.
This is motivated by the observed masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
probed by $\CII$ line width estimation \citep{2019ApJ...872L..29S}.
Therefore, we sample base halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6. 
We then generate 10$^4$ merger trees with each base halo mass backward in time using the {\tt GALFORM} 
semi-analytic algorithm based on the extended Press-Schechter formalism 
\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}.
The normalizations of the merger trees are estimated by the base halo number densities from Sheth-Tormen halo mass function \citep{2001MNRAS.323....1S}:
%%%%%%%
%    Eq. 1
%%%%%%%
\begin{equation}
n_{\Mh}= \int_{\Mh}^{10\Mh}  \frac{\D n_{\mathrm{ST}}} {\D \Mh} \D \Mh.
\label{eq:nST}
\end{equation}

@@

Next we introduce our seeding model where the gas dynamical and thermal evolution is regulated by the parent halo growth histories, 
and the environmental streaming velocities.
In \citet{2021ApJ...917...60L}, we propose an semi-analytical model which 
traces the gas evolution along its parent halo growth and yields the seed BH mass distribution. 
% The background UV radiation $$ is calculated by semi-analytical arguments of men
The merger heating and enhancement of background Lyman-Werner radiation intensity $\jlw$ 
due to halo clustering is taken into account to shape the gas thermal evolution. 
Besides, the baryonic streaming velocity $\vbsm$ together with the turbulent velocity $v_\mathrm{tur}$ 
through halo virialization is modeled by the effective sound speed of gas:
%%%%%%%
%    Eq. 2
%%%%%%%
\begin{equation}
  c_{\rm eff} = \sqrt{ c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2}, 
\end{equation}
where the coefficient $\alpha_0$ is suggested to be in order of unity by previous studies 
\citep{2017Sci...357.1375H,2019MNRAS.484.3510S} 
and we apply $\alpha_0 = 1$ in this work. 
Following this model we produce 10$^4$ BH seeds with their formation time and masses $M_\mathrm{seed}$, 
in each merger tree with a given $\vbsm$. 
Contributed by the number densities of the base halos and the fraction of environmental $\vbsm$, 
we construct the seed BH mass distribution shown in Fig.~\ref{fig:seedmf}.

@@

% Figure 1 shows the BH seeds formed in progenitors of $\Mh = 10^{11}, 10^{12}$
\vspace{2mm}
\subsection{BH growth \& mass Function}\label{sec:MF}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. We have constraints on simulations and observations of lower redshift counterparts.
With seeds planted, we grow the BHs with a semi-analytical accretion rate model 
and study the BH mass distribution at redshift 6. 
The growth model is captured by a limited number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by: 
%%%%%%%
%    Eq. 3
%%%%%%%
\begin{equation}
  \label{eq:mdot}
  \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd},
\end{equation}
where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
$\lambda = L/L_\mathrm{Edd}$ is the Eddington ratio that represents the strength of the accretion power.
Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $ according to the thin accretion disk model 
\citep{1973A&A....24..337S}, which is also consistent with 
the Soltan's argument  \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
% The high mass BH should be strangulated by as it grows, 
We introduce the mass dependency 
$f(M) = 0.5 \left[1+\left(M/10^8~\Msun\right)^\delta\right] ^ {-1}$, 
to suppress the high mass BH growth with a positive $\delta$. With decreasing $\delta$, 
the model is reduced to an exponential growth independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.

The quasar activity is episodic in nature, with bursts of accretion triggered by gas inflows 
% \citep[e.g., mergers or disk instabilities, see][]{2005Natur.433..604D,2005ApJ...630..705H}, 
\citep{2005Natur.433..604D,2005ApJ...630..705H}, 
and the accretion rate declines with self-regulating feedbacks \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} or 
self-similar disk evolution \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}.
This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity in the Eddington ratios 
of a quasar sample, where the Eddington ratio distribution function (ERDF) $\D P/ \D\ln\lambda$ shares the same Schechter function shape 
with the differential time at different $\lambda$ \citep{2006ApJ...639..700H,2009ApJ...698.1550H}.
Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
\citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}, 
therefore we take 2 free parameters $\lambda_0$ and $\alpha$ to characterize the ERDF:
%%%%%%%
%    Eq. 4
%%%%%%%
\begin{equation}
  \label{eq:Pl}
  \frac{\D P}{ d\ln \lambda} \propto
  \left(\frac{\lambda} {\lambda_0} \right)^\alpha \exp{\left(-\frac{\lambda}{\lambda_0}\right)},
\end{equation}
normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
The minimum Eddington ratio $\lambda_\mathrm{min}$ is motivated by the behavior of quasar luminosity evolution 
that decreases mildly toward $\lambda\sim 0.1-0.01$ with $\lesssim$ 100 Myr after activation \citep{2011ApJ...737...26N}, 
also suggested by a turnover at the lowest $\lambda\lesssim 0.01-0.001$ on the observational side \citep{2018MNRAS.474.1225A}.

@@

Next, we explain our method to calculate the time evolution of BHMF, 
which is given by combining the BH mass distribution from the seeds growing independently in merger trees
with different base halo mass $\Mh$,
weighted by the environmental $\vbsm$ probability and seeding fraction: 
%%%%%%%
%    Eq. 5
%%%%%%%
\begin{align}
& \Phi_\mathrm{M} \equiv \frac{\D n}{\D \log M}  \nonumber \\
& =\sum_{\Mh}\sum_{\vbsm} n_{\Mh} f_{\vbsm} {\fseed} \left(\frac{\D P}{\D \log M}\right)_{\Mh, \vbsm}.
\end{align}

For a given combination of $\Mh$ and $\vbsm$, 
We then calculate the BH mass distribution $\D P/\D\log M$ iteratively 
at a series of checkpoints with an interval of $\tlife$, 
from the earliest seed formation time to $z=$ 6. 
% we set a total number of $\Nt$ checkpoints with an interval of $\tlife$,
% where $\Nt = \lfloor \left(t_\mathrm{H}(z=6) - t_\mathrm{H}(z_\mathrm{seed,max})\right)/ \tlife \rfloor$, 
At each checkpoint $t$, the BH mass distribution is developed from the growth of itself 
at the previous checkpoint, plus the seeds newly formed in between.
Considering the growth of a BH with mass $M_{\rm i}$ by a time interval $\Delta t$, 
from the accretion rate prescription in Eq.~(\ref{eq:mdot}), the final mass $M$ can be described in the relation 
%%%%%%%
%    Eq. 6
%%%%%%%
\begin{equation}
  \label{eq:mi2m}
  \ln \left(\frac{M} {M_{\rm i}}\right) + \frac{1}{\delta} 
  \left[ \left(\frac{M}{M_0}\right)^\delta - \left(\frac{M_{\rm i}}{M_0}\right)^\delta \right]
  = \frac{\lambda \Delta t}{\tEdd}.
\end{equation}

This yields the BH mass distribution 
%%%%%%%
%    Eq. 7
%%%%%%%
\begin{align}
  \label{eq:dpdm}
  & \frac{\D P}{\D \log M} = \int_{}^{} 
   \left(\frac{\D P}{\D \ln \lambda}\right)_{\lambda(M, M_\mathrm{i},\Delta t, \delta)} \nonumber \\
  & \left(\frac{\D \ln \lambda}{\D \log M} \right)_{M, M_\mathrm{i},\Delta t, \delta}
  \frac{\D P}{\D \log M_\mathrm{i}} \D\log M_\mathrm{i},
\end{align}
where ${\D P}/{\D \ln\lambda}$ is given by a set of parameters $\lambda_0$ and $\alpha$ in Eq.~(\ref{eq:Pl}), 
at the $\lambda$ value $\lambda\left(M, M_\mathrm{i},\Delta t, \delta\right)$ inferred from Eq.~(\ref{eq:mi2m}).
For the evolution of the BH mass distribution, we set $\Delta t=\tlife$.
On the other hand, for the growth of an individual seed, 
$\Delta t < \tlife$ is calculated from the seeding time to the current checkpoint,
and $ \D P/\D \log M_\mathrm{i}$ is a discrete function which is 10$^{-4}$ 
(normalized by the track numbers 10$^4$ in a merger tree) at $M_\mathrm{i} = M_\mathrm{seed}$, 
and 0 elsewhere.
This procedure is illustrated schematically in Fig.~\ref{fig:scheme}.

@@

\vspace{2mm}
\subsection{QLF after obscuration}\label{sec:LF}
Furthermore, we can generate QLFs that is directly probed by high-$z$ observations.
%  compared with observations and in return constrain our model.
For a BH accreting with bolometric luminosity $\Lbol=\lambda L_\mathrm{Edd}$, 
its absolute magnitude $\Muv$ in the rest-frame ultraviolet (UV) band is given by:
%%%%%%%
%    Eq. 8
%%%%%%%
\begin{equation}
  \label{eq:M1450}
  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right).
\end{equation}
Here we adopt the bolometric correction factor $\fbol=4.4$ for the monochromatic UV band \citep{2006ApJS..166..470R}.
Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
the quasar abundances with different luminosities. 
However, we note that a vital ingredient to construct the observed QLF, 
is the luminosity dependent obscuration fraction, 
which decreases the fraction of the detectable quasars toward the dimmer population 
\citep{2003ApJ...598..886U,2014ApJ...786..104U,2008A&A...490..905H,2014MNRAS.437.3550M}, 
thus differs the normalization and shape of the observed QLF from the intrinsic one.

@@

After taking obscuration into account, the observed luminosity function for a given BHMF and ERDF can be written as:
%%%%%%%
%    Eq. 9
%%%%%%%
\begin{align}
\label{eq:dn_dM1450}
& \Phi_\mathrm{\Muv} \equiv \frac{\D n}{\D \Muv} \nonumber \\
& = \left[1 -\fobsc\left(\Muv\right) \right] \times % \nonumber \\
\int_{}^{} \left(\frac{\D P}{\D \ln \lambda}\right)_{\lambda(\Muv, M)}  \nonumber \\
& \left(\frac{\D \ln \lambda}{\D \Muv} \right)_{\Muv, M} \Phi_\mathrm{M} \D \log M,
\end{align}
where $\lambda\left(\Muv,M\right)$ is the obtained from Eq.~(\ref{eq:M1450}).
%
Hence the observed QLF can be produced simultaneously with the BHMF from a set of model paramters, 
to be compared with the ones from observation.

@@

% 3. posterior
% Then evaluating the likelihood of the dataset reproducing the observed BHMF and QLF at $z=$ 6, 
% the Markov chain of samples converges to the best-fit (maximum likelihood) parameters.
Following the prior distribution, parameters are sampled to generate the synthetic BHMF and QLF dataset, 
which is then conjointly compared with the observational data. 
The offset between the model and data is evaluated as 
%%%%%%%
%    Eq. 10
%%%%%%%
\begin{align}
  \chi^2 = \sum_i
  \frac{\left(\log{\Phi_\mathrm{mod,i}} - \log{\Phi_\mathrm{obs,i}}\right)^2}{(\log{\Phi_\mathrm{err,i}})^2},
\end{align}
where $\Phi_\mathrm{mod,i}$ and $\Phi_\mathrm{obs,i}$ 
represent the modeled and observational values of $\Phi_\mathrm{M}$ ($\Phi_\mathrm{\Muv}$) in the \textit{i-}th BHMF (QLF) bin, and 
$\Phi_\mathrm{err,i}$ is the corresponding error.
Note that the equal constraints from the BHMF and QLF are realized by extracting
comparable numbers of data bins from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
% the constraint is actually insensitive to the choice of bin numbers. 
The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
with the models best reproducing the $z=$ 6 BHMF and QLF.

>>>>

\vspace{2mm}
\subsection{Seeds}\label{sec:seed}
The QLFs at high redshifts are determined by the original BH seeding and subsequent growth. 
Firstly we describe our model regarding the formation of BH seeds in progenitor DM halos 
that end up in high-$z$ quasar host galaxies with halo masses of $\Mh>10^{11}~\Msun$.
This is motivated by the observed masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
probed by \blue{$\CII$ line width estimation} \citep{2019ApJ...872L..29S}.
Therefore, we sample base halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6. 
We then generate 10$^4$ merger trees with each base halo mass backward in time using the {\tt GALFORM} 
semi-analytic algorithm based on the extended Press-Schechter formalism 
\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}, and study the BH seeds formed therein.

@@

Next we introduce our seeding model where the gas dynamical and thermal evolution is regulated by the parent halo growth histories, 
and the environmental streaming velocities.
In \citet{2021ApJ...917...60L}, we propose an semi-analytical model which 
traces the gas evolution along its parent halo growth and yields the seed BH mass distribution. 
% The background UV radiation $$ is calculated by semi-analytical arguments of men
The merger heating and enhancement of background Lyman-Werner radiation intensity $\jlw$ 
due to halo clustering is taken into account to shape the gas thermal evolution. 
Besides, the baryonic streaming velocity $\vbsm$ together with the turbulent velocity $v_\mathrm{tur}$ 
through halo virialization is taken into account
\footnote{
We model the effective sound speed of gas as $c_{\rm eff} = \sqrt{ c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2}$,
where the coefficient $\alpha_0 = 1$ is motivated by previous studies 
\citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
}.
Following this model we produce 10$^4$ BH seeds with their formation time and masses, 
in each merger tree with a given $\vbsm$, 
the abundance of seeds is normalized with the base halo number density from the Sheth-Tormen \citep{2001MNRAS.323....1S} halo mass function:
\begin{align*}
  n_{\Mh}= \int_{\Mh}^{10\Mh}  \frac{\D n_{\mathrm{ST}}} {\D \Mh} \D \Mh, 
\end{align*}
weighted by the environmental $\vbsm$ fraction $f_{\vbsm}$. 
We then construct the seed BH mass distribution shown in Fig.~\ref{fig:seedmf}.

@@

% Figure 1 shows the BH seeds formed in progenitors of $\Mh = 10^{11}, 10^{12}$
\vspace{2mm}
\subsection{BH growth \& mass Function}\label{sec:MF}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. We have constraints on simulations and observations of lower redshift counterparts.
With seeds planted, we grow the BHs with a semi-analytical accretion rate model 
and study the BH mass distribution at redshift 6. 
\blue{(references + discussion)}
The growth model is captured by a limited number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by: 
%%%%%%%
%    Eq. 1
%%%%%%%
\begin{equation}
  \label{eq:mdot}
  \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd},
\end{equation}
where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
$\lambda = L/L_\mathrm{Edd}$ is the Eddington ratio that represents the strength of the accretion power.
Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $ according to the thin accretion disk model 
\citep{1973A&A....24..337S}, which is also consistent with 
the Soltan's argument  \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
% The high mass BH should be strangulated by as it grows, 
We introduce the mass dependency 
$f(M) = 0.5 \left[1+\left(M/10^8~\Msun\right)^\delta\right] ^ {-1}$, 
to suppress the high mass BH growth with a positive $\delta$. 
\blue{(references)}
With decreasing $\delta$, 
the model is reduced to an exponential growth independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.

The quasar activity is episodic in nature, with bursts of accretion triggered by gas inflows 
% \citep[e.g., mergers or disk instabilities, see][]{2005Natur.433..604D,2005ApJ...630..705H}, 
\citep{2005Natur.433..604D,2005ApJ...630..705H}, 
and the accretion rate declines with self-regulating feedbacks \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} or 
self-similar disk evolution \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}.
This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity in the Eddington ratios 
of a quasar sample, where the Eddington ratio distribution function (ERDF) $\D P/ \D\ln\lambda$ shares the same Schechter function shape 
with the differential time at different $\lambda$ \citep{2006ApJ...639..700H,2009ApJ...698.1550H}.
Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
\citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}, 
therefore we take 2 free parameters $\lambda_0$ and $\alpha$ to characterize the ERDF:
%%%%%%%
%    Eq. 2
%%%%%%%
\begin{equation}
  \label{eq:Pl}
  \frac{\D P}{ d\ln \lambda} \propto
  \left(\frac{\lambda} {\lambda_0} \right)^\alpha \exp{\left(-\frac{\lambda}{\lambda_0}\right)},
\end{equation}
normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
The minimum Eddington ratio $\lambda_\mathrm{min}$ is motivated by the behavior of quasar luminosity evolution 
that decreases mildly toward $\lambda\sim 0.1-0.01$ with $\lesssim$ 100 Myr after activation \citep{2011ApJ...737...26N}, 
also suggested by a turnover at the lowest $\lambda\lesssim 0.01-0.001$ on the observational side \citep{2018MNRAS.474.1225A}.

@@

Next, we explain our method to calculate the time evolution of BHMF, 
which is given by combining the BH mass distribution from the seeds growing independently in merger trees
with different base halo mass $\Mh$,
weighted by the environmental $\vbsm$ probability and seeding fraction: 
%%%%%%%
%    Eq. 3
%%%%%%%
\begin{align}
& \Phi_\mathrm{M} \equiv \frac{\D n}{\D \log M}  \nonumber \\
& =\sum_{\Mh}\sum_{\vbsm} n_{\Mh} f_{\vbsm} {\fseed} \left(\frac{\D P}{\D \log M}\right)_{\Mh, \vbsm}.
\end{align}

For a given combination of $\Mh$ and $\vbsm$, 
We then calculate the BH mass distribution $\D P/\D\log M$ iteratively 
at a series of checkpoints with an interval of $\tlife$, 
from the earliest seed formation time to $z=$ 6. 
% we set a total number of $\Nt$ checkpoints with an interval of $\tlife$,
% where $\Nt = \lfloor \left(t_\mathrm{H}(z=6) - t_\mathrm{H}(z_\mathrm{seed,max})\right)/ \tlife \rfloor$, 
At each checkpoint $t$, the BH mass distribution is developed from the growth of itself 
at the previous checkpoint, plus the seeds newly formed in between.
Considering the growth of a BH with mass $M_{\rm i}$ by a time interval $\Delta t$, 
from the accretion rate prescription in Eq.~(\ref{eq:mdot}), the final mass $M$ can be described in the relation 
%%%%%%%
%    Eq. 4
%%%%%%%
\begin{equation}
  \label{eq:mi2m}
  \ln \left(\frac{M} {M_{\rm i}}\right) + \frac{1}{\delta} 
  \left[ \left(\frac{M}{M_0}\right)^\delta - \left(\frac{M_{\rm i}}{M_0}\right)^\delta \right]
  = \frac{\lambda \Delta t}{\tEdd}.
\end{equation}

This yields the BH mass distribution 
%%%%%%%
%    Eq. 5
%%%%%%%
\begin{align}
  \label{eq:dpdm}
  & \frac{\D P}{\D \log M} = \int_{}^{} 
   \left(\frac{\D P}{\D \ln \lambda}\right)_{\lambda(M, M_\mathrm{i},\Delta t, \delta)} \nonumber \\
  & \left(\frac{\D \ln \lambda}{\D \log M} \right)_{M, M_\mathrm{i},\Delta t, \delta}
  \frac{\D P}{\D \log M_\mathrm{i}} \D\log M_\mathrm{i},
\end{align}
where ${\D P}/{\D \ln\lambda}$ is given by a set of parameters $\lambda_0$ and $\alpha$ in Eq.~(\ref{eq:Pl}), 
at the $\lambda$ value $\lambda\left(M, M_\mathrm{i},\Delta t, \delta\right)$ inferred from Eq.~(\ref{eq:mi2m}).
For the evolution of the BH mass distribution, we set $\Delta t=\tlife$.
On the other hand, for the growth of an individual seed, 
$\Delta t < \tlife$ is calculated from the seeding time to the current checkpoint,
and $ \D P/\D \log M_\mathrm{i}$ is a discrete function which is 10$^{-4}$ 
(normalized by the track numbers 10$^4$ in a merger tree) at $M_\mathrm{i} = M_\mathrm{seed}$, 
and 0 elsewhere.
This procedure is illustrated schematically in Fig.~\ref{fig:scheme}.

@@

\vspace{2mm}
\subsection{QLF after obscuration}\label{sec:LF}
Furthermore, we can generate QLFs that is directly probed by high-$z$ observations.
%  compared with observations and in return constrain our model.
For a BH accreting with bolometric luminosity $\Lbol=\lambda L_\mathrm{Edd}$, 
its absolute magnitude $\Muv$ in the rest-frame ultraviolet (UV) band is given by:
%%%%%%%
%    Eq. 6
%%%%%%%
\begin{equation}
  \label{eq:M1450}
  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right).
\end{equation}
Here we adopt the bolometric correction factor $\fbol=4.4$ for the monochromatic UV band \citep{2006ApJS..166..470R}.
Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
the quasar abundances with different luminosities. 
However, we note that a vital ingredient to construct the observed QLF, 
is the luminosity dependent obscuration fraction, 
which decreases the fraction of the detectable quasars toward the dimmer population 
\citep{2003ApJ...598..886U,2014ApJ...786..104U,2008A&A...490..905H,2014MNRAS.437.3550M}, 
thus differs the normalization and shape of the observed QLF from the intrinsic one.

@@

After taking obscuration into account, the observed luminosity function for a given BHMF and ERDF can be written as:
%%%%%%%
%    Eq. 7
%%%%%%%
\begin{align}
\label{eq:dn_dM1450}
& \Phi_\mathrm{\Muv} \equiv \frac{\D n}{\D \Muv} \nonumber \\
& = \left[1 -\fobsc\left(\Muv\right) \right] \times % \nonumber \\
\int_{}^{} \left(\frac{\D P}{\D \ln \lambda}\right)_{\lambda(\Muv, M)}  \nonumber \\
& \left(\frac{\D \ln \lambda}{\D \Muv} \right)_{\Muv, M} \Phi_\mathrm{M} \D \log M,
\end{align}
where $\lambda\left(\Muv,M\right)$ is the obtained from Eq.~(\ref{eq:M1450}).
%
Hence the observed QLF can be produced simultaneously with the BHMF from a set of model paramters, 
to be compared with the ones from observation.

@@

% 3. posterior
% Then evaluating the likelihood of the dataset reproducing the observed BHMF and QLF at $z=$ 6, 
% the Markov chain of samples converges to the best-fit (maximum likelihood) parameters.
Following the prior distribution, parameters are sampled to generate the synthetic BHMF and QLF dataset, 
which is then conjointly compared with the observational data. 
The offset between the model and data is evaluated as 
%%%%%%%
%    Eq. 8
%%%%%%%
\begin{align}
  \chi^2 = \sum_i
  \frac{\left(\log{\Phi_\mathrm{mod,i}} - \log{\Phi_\mathrm{obs,i}}\right)^2}{(\log{\Phi_\mathrm{err,i}})^2},
\end{align}
where $\Phi_\mathrm{mod,i}$ and $\Phi_\mathrm{obs,i}$ 
represent the modeled and observational values of $\Phi_\mathrm{M}$ ($\Phi_\mathrm{\Muv}$) in the \textit{i-}th BHMF (QLF) bin, and 
$\Phi_\mathrm{err,i}$ is the corresponding error.
Note that the equal constraints from the BHMF and QLF are realized by extracting
comparable numbers of data bins from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
% the constraint is actually insensitive to the choice of bin numbers. 
The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
with the models best reproducing the $z=$ 6 BHMF and QLF.
